Code to reproduce results in _Semi-parametric generalized linear model for

### 2022-03-20 ManuscriptCode/Manuscript.Rmd
Save plot data for Zenodo upload

@@

scomb <- comb_beta %>%
  group_by(Generator, Term, Model) %>%
  summarize(bias = mean(Est-Correct, na.rm=TRUE),
            mc.se = sd(Est, na.rm=TRUE),
            se = mean(SE, na.rm=TRUE),
            .groups="drop_last") %>%
  mutate(rel.eff = mc.se / mc.se[Model=="GEE"]) %>%
  ungroup() %>%
  arrange(Generator, Model, Term)
kable(scomb, digits=3)
```

@@

@@

>>>>

# save data
write.csv(fits %>% select(Model, Trt, ClusterSize, NResp, Prob),
          file="PredictPlot.csv")

@@

scomb <- comb_beta %>%
  group_by(Generator, Term, Model) %>%
  summarize(bias = mean(Est-Correct, na.rm=TRUE),
            mc.se = sd(Est, na.rm=TRUE),
            se = mean(SE, na.rm=TRUE),
            .groups="drop_last") %>%
  mutate(rel.eff = mc.se^2 / mc.se[Model=="GEE"]^2) %>%
  ungroup() %>%
  arrange(Generator, Term, Model)
kable(scomb, digits=3)
```

@@

# save data
write.csv(comb_beta %>% select(Generator, ID, Model, Coefficient, Est, SE, Correct),
          file="ComparePlot.csv")
```

@@

# save data
write.csv(comb_pdf %>% select(Generator, ID, Model, NResp, Est, Correct),
          file="PDFPlot.csv")
```
